% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TEX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,10pt,oneside]{article}
%\documentclass[letterpaper,10pt,oneside]{article}

% Do not stop on errors during compilation.
\nonstopmode

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{Adam Fidel}

\begin{subtitle}
{Department of Computer Science and Engineering, Texas A\&M University, College Station, TX 77843-3112}
\par
\href{mailto:refuse@gmail.com}
{refuse@gmail.com}
\,$\bullet$\,
+1\,(469)\,387-3025
\,$\bullet$\,
\href{https://ledif.me}
{https://ledif.me}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section{Education}
{Education}

\href{http://www.tamu.edu}
{\textbf{Texas A\&M University}},
College Station, TX, USA

\SmallEntryGap
Doctor of Philosophy (Ph.D.) in
\href{http://cse.tamu.edu}
{Computer Science}
\hfill
\DatestampYMD{2010}{08}{15} --
Present
\begin{detail}
\begin{detail}
Cumulative GPA: 4.0 / 4.0
\end{detail}
Advisors:
Professors Nancy Amato and Lawrence Rauchwerger
\par
Research areas:
High performance computing, parallel algorithms, \par
\hskip 7.3em parallel graph processing.
\par
Dissertation: \emph{Bounded Asynchrony and Nested Parallelism for } \par
\hskip 6.0em \emph{Scalable Graph Processing}
\end{detail}

\EntryGap
\href{http://www.ttu.edu}
{\textbf{Texas Tech University}},
Lubbock, TX, USA
\par
Bachelor of Science (B.S.) in
\href{http://cs.ttu.edu}
{Computer Science}
\hfill
\DatestampYMD{2006}{08}{15} --
\DatestampYMD{2010}{05}{15}
\begin{detail}
Summa Cum Laude
\par
Cumulative GPA: 4.0 / 4.0
\end{detail}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %% ACADEMIC HONORS & AWARDS %%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Honors \& Awards}
{Honors\newline
\& Awards}

Best Paper Finalist - PACT
\hfill
\DatestampY{2015}

Best Paper Award - PACT
\hfill
\DatestampY{2014}

2\textsuperscript{nd} Place of Texas A\&M IAP Research Poster Contest
\hfill
\DatestampY{2014}

Texas A\&M Graduate Diversity Fellowship
\hfill
\DatestampY{2010}--\DatestampY{2013}

Teaching Assistant Teaching Excellence Award - Texas A\&M University
\hfill
\DatestampY{2012}

CRA-W/CDC Distributed Research Experiences for Undergraduates
\hfill
\DatestampY{2009}

Engineering Scholarship,
Baker Hughes
\hfill
\DatestampY{2008}

CRA-W/CDC Distributed Research Experiences for Undergraduates
\hfill
\DatestampY{2008}

Texas Tech ACM Junior of the Year
\hfill
\DatestampY{2008}

Scholarship in Computer Science,
Raytheon
\hfill
\DatestampY{2007}

President's List
\hfill
\DatestampY{2006} --
\DatestampY{2010}



% %%%%%%%%%%%%%%%%%%%%%%%%%
% %% WORK EXPERIENCE %%
% %%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
{Experience}


\textbf{Google},
Mountain View, CA, USA
\par
Software Engineer, Ph.D. Intern
\hfill
\DatestampYMD{2015}{09}{28} --
\DatestampYMD{2015}{12}{20}
\begin{detail}
Member of the search infrastructure team.
\par
 Designed and implemented parallel graph mining algorithms for massive scale graphs.
 \par
\end{detail}
\EntryGap


% %%%%%%%%%%%%%%%%%%%%%%%%%
% %% RESEARCH EXPERIENCE %%
% %%%%%%%%%%%%%%%%%%%%%%%%%


\textbf{Texas A\&M University - Parasol Lab}, College Station, TX, USA
\par
Research Assistant
\hfill
\DatestampYMD{2010}{05}{15} --
Present
\begin{detail}
Developer of STAPL, a parallel superset of the C++ Standard Template Library.
\par
\href{http://parasol-lab.gitlab.io/stapl-home}{http://parasol-lab.gitlab.io/stapl-home}
\par
\emph{Advisors}: Professors Nancy Amato and Lawrence Rauchwerger
\par
\end{detail}
\EntryGap

\textbf{University of Massachusetts, Amherst}, Amherst, MA, USA
\par
Undergraduate Research Assistant
\hfill
\DatestampYMD{2009}{05}{15} --
\DatestampYMD{2009}{08}{30}
\begin{detail}
Automatic compiler backend generation targeting JikesRVM.
\par
\emph{Advisor}: Professor J. Eliot B. Moss
\par
\end{detail}


% %%%%%%%%%%%%%%%%%%
% %% PUBLICATIONS %%
% %%%%%%%%%%%%%%%%%%

\section{Publications}
{Peer Reviewed Publications}

% \BibSpace{Ioannis Papadopoulos, Nathan Thomas, \underline{Adam Fidel}, Nancy M. Amato, Lawrence Rauchwerger, ``STAPL-RTS: An Application Driven Runtime System,'' In \textit{International Conference on Supercomputing (ICS)}, Newport Beach, California, USA,
%
% \EntryGap
% \BibSpace
% \href{http://www.example.com/my-paper-doi-1}
% {\underline{J.~Doe} and J.~Citizen,
% ``Measuring the extent of climate change,''
% in \textit{Proceedings of the International Climate Change Conference},
% London, UK,
% \DatestampYM{2005}{11}.}


{\underline{Adam Fidel}, Francisco Coral Sabido, Colton Riedel, Nancy M. Amato, Lawrence Rauchwerger, ``Fast Approximate Distance Queries in Unweighted Graphs using Bounded Asynchrony,'' In Wkshp. on Lang. and Comp. for Par. Comp. (LCPC), Rochester, NY, USA, September 2016.}

\EntryGap
{{\bf Best Paper Finalist.} Harshvardhan, \underline{Adam Fidel}, Nancy M. Amato, Lawrence Rauchwerger, ``An Algorithmic Approach to Communication Reduction in Parallel Graph Algorithms,'' In Proc. Int. Conf. on Par. Arch. and Comp. Tech. (PACT), San Francisco, CA, USA, November 2015.}

\EntryGap

{Ioannis Papadopoulos, Nathan Thomas, \underline{Adam Fidel}, Dielli Hoxha, Nancy M. Amato, Lawrence Rauchwerger, ``Asynchronous Nested Parallelism for Dynamic Applications in Distributed Memory,'' In Wkshp. on Lang. and Comp. for Par. Comp. (LCPC), Raleigh, NC, USA, September 2015.}

\EntryGap

{Ioannis Papadopoulos, Nathan Thomas, \underline{Adam Fidel}, Nancy M. Amato, Lawrence Rauchwerger, ``STAPL-RTS: An Application Driven Runtime System,'' In \textit{International Conference on Supercomputing (ICS)}, Newport Beach, California, USA, \DatestampYM{2015}{06}.}

\EntryGap

{Harshvardhan, Brandon West, \underline{Adam Fidel}, Nancy M. Amato, Lawrence Rauchwerger, ``A Hybrid Approach To Processing Big Data Graphs on Memory-Restricted Systems,'' In Proc. Int. Par. and Dist. Proc. Symp. (IPDPS), Hyderabad, India, May 2015.}

\EntryGap

{{\bf Best Paper Award}. Harshvardhan, \underline{Adam Fidel} Nancy M. Amato, Lawrence Rauchwerger, ``KLA: A New Algorithmic Paradigm for Parallel Graph Computations,'' In Proc. Int. Conf. on Par. Arch. and Comp. Tech. (PACT), Edmonton, Alberta, Canada, Aug 2014.}

\EntryGap

{\underline{Adam Fidel}, Sam Ade Jacobs, Shishir Sharma, Nancy M. Amato, Lawrence Rauchwerger, ``Using Load Balancing to Scalably Parallelize Sampling-Based Motion Planning Algorithms,'' In Proc. Int. Par. and Dist. Proc. Symp. (IPDPS), Phoenix, Arizona, USA, May 2014.}

\EntryGap

{Harshvardhan, \underline{Adam Fidel}, Nancy Amato and Lawrence Rauchwerger ``The STAPL Graph Library''. In Wkshp. on Lang. and Comp. for Par. Comp. (LCPC), Tokyo, Japan, Sep 2012, pp. 46-60.}

\EntryGap

{Gabriel Tanase, Antal Buss, \underline{Adam Fidel}, Harshvardhan, Ioannis Papadopoulos, Olga Pearce, Timmie Smith, Nathan Thomas, Xiabing Xu, Nedhal Mourad, Jeremy Vu, Mauro Bianco, Nancy M. Amato, Lawrence Rauchwerger ``The STAPL Parallel Container Framework''. In Proc. ACM SIGPLAN Symp. Prin. Prac. Par. Prog. (PPoPP), Feb 2011, pp. 235-246.}

\EntryGap

{Antal Buss, \underline{Adam Fidel}, Harshvardhan, Timmie Smith, Gabriel Tanase, Nathan Thomas, Xiabing Xu, Mauro Bianco, Nancy M. Amato, Lawrence Rauchwerger. ``The STAPL pView''. In Wkshp. on Lang. and Comp. for Par. Comp. (LCPC), Houston, Texas, Oct 2010, pp. 261-275.}

\EntryGap

\section{OtherPublications}
{Other Publications}

{\underline{Adam Fidel}, Nancy M. Amato, Lawrence Rauchwerger, ``Bounded Asynchrony and Nested Parallelism for Scalable Graph Processing,''
Doctoral Showcase at International Conference for High Performance Computing, Networking, Storage, and Analysis (SC17), Denver, Colorado, USA, November 2017.}

\EntryGap

{\underline{Adam Fidel}, Harshvardhan, Nancy M. Amato, Lawrence Rauchwerger, ``SGL: An Approach for Future Exascale Graph Processing,''
invited talk at Runtime Systems for Extreme Scale Programming Models and Architectures (RESPA), Salt Lake City, UT, USA, Nov 2016}

\EntryGap

{\underline{Adam Fidel}, Nancy M. Amato, Lawrence Rauchwerger, ``From Petascale to the Pocket: Adaptively Scaling Parallel Programs for Mobile SoCs,'' poster
session presented at Int. Par. and Dist. Proc. Symp. (IPDPS) PhD Forum, Phoenix, Arizona, USA, May 2014}

\EntryGap


{\underline{Adam Fidel}, Sam Ade Jacobs, Shishir Sharma, Lawrence Rauchwerger, Nancy M. Amato, ``Load Balancing Techniques for Scalable Parallelization of Sampling-Based Motion Planning Algorithms,'' Technical Report, TR13-002 , Parasol Laboratory, Department of Computer Science, Texas A\&M University, Mar 2013.}

\EntryGap


{Antal Buss, Timmie Smith, Gabriel Tanase, Natham Thomas, Lena Olson, \underline{Adam Fidel}, Mauro Bianco, Nancy M. Amato, Lawrence Rauchwerger ``Design for interoperability in STAPL: pMatrices and linear algebra algorithms''. Technical Report TR08-003, Dept. of Computer Science, Texas A\&M University, August 2008.}

% %%%%%%%%%%%%%%%%%%%%%%%%%
% %% TEACHING EXPERIENCE %%
% %%%%%%%%%%%%%%%%%%%%%%%%%

\section{Teaching Experience}
{Teaching Experience}

{\textbf{Texas A\&M University}},
College Station, TX, USA
\par
Teaching Assistant, Spring 2017
\hfill
\DatestampY{2017} --
\DatestampY{2017}
\begin{detail}
CSCE 605 -- Compiler Design (graduate)
\end{detail}

\EntryGap


{\textbf{Texas A\&M University}},
College Station, TX, USA
\par
Teaching Assistant, Spring 2012 and Spring 2013
\hfill
\DatestampY{2012} --
\DatestampY{2013}
\begin{detail}
CSCE 221 -- Data Structures and Algorithms (honors section)
\end{detail}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL AFFILIATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Peer Reviewer}
{Peer Reviewer}

SIGPLAN Conference on Principles and Practice of Parallel Programming (PPoPP)
\par ACM International Conference on Supercomputing (ICS)
\par ACM Programming Language Design and Implementation (PLDI)
\par International Conference on Parallel Architectures and Compilation Techniques (PACT)
\par IEEE International Parallel \& Distributed Processing Symposium (IPDPS)
\par Wkshp. on Languages and Compilers for Parallel Computing (LCPC)
\par International Systems and Storage Conference (SYSTOR)
\par High Performance Computing Conference (HiPC)
\par Int'l Symp. on Computer Architecture and High Performance Computing (SBAC-PAD)


\section{Professional Activities}
{Professional Activities}

{\textbf{A Festschrift for Bjarne Stroustrup}, College Station, TX, USA }
\par
Student Volunteer
\hfill
\DatestampY{2012}

\EntryGap


{\textbf{Parallel Architectures and Compilation Techniques}, Galveston Island, TX, USA }
\par
Student Volunteer
\hfill
\DatestampY{2011}


\EntryGap

{\textbf{Association for Computing Machinery}}
\par
Student Member
\hfill
\DatestampY{2010} --
Present

\EntryGap
{\textbf{Institute of Electrical and Electronics Engineers }}
\par
Student Member
\hfill
\DatestampY{2010} --
Present

% %%%%%%%%%%%%%%%%%%%%%%%
% %% CAMPUS ACTIVITIES %%
% %%%%%%%%%%%%%%%%%%%%%%%

% \section{Campus Activities}
% {Campus Activities}

% \href{http://www.example.com/my-club}
% {\textbf{First Volunteers Club}},
% First American University
% \par
% President
% \hfill
% \DatestampYMD{2006}{08}{15} --
% \DatestampYMD{2007}{08}{15}
% \begin{detail}
% Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur vitae laoreet velit, vel ultricies est. Nam nec elit ac ante facilisis ultrices. Integer sit amet turpis dolor. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nunc at orci eu leo vulputate finibus sed et sem. Suspendisse volutpat sapien et mi cursus, gravida ornare mauris sollicitudin.
% \end{detail}

% %%%%%%%%%%%%%%%
% %% LANGUAGES %%
% %%%%%%%%%%%%%%%

% \section{Languages}
% {Languages}

% English: Native language.
% \par
% Spanish: Fluent (speaking, reading, writing).
% \par
% Latin: Intermediate (reading); basic (speaking, writing).


%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section{Skills}
{Skills}

C++ (\emph{Boost, STL}), MPI, OpenMP, Javascript (\emph{Node, React}), R, Python, Fortran
\par
\EntryGap
https://github.com/ledif/
\par
\EntryGap
https://gitlab.com/ledif/

% %%%%%%%%%%%%%%%
% %% INTERESTS %%
% %%%%%%%%%%%%%%%

% \section{Interests}
% {Interests}

% Digital photography,
% typography,
% swimming.


% Footer
\EntryGap
\EntryGap
\EntryGap

  \begin{small}
    Last updated: \today
  \end{small}


\end{body}

\end{document}
