% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TEX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,10pt,oneside]{article}
%\documentclass[letterpaper,10pt,oneside]{article}

% Do not stop on errors during compilation.
\nonstopmode

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{Adam Fidel}

\begin{subtitle}
{Department of Computer Science and Engineering, Texas A\&M University, College Station, TX 77843-3112}
\par
\href{mailto:fidel@cse.tamu.edu}
{fidel@cse.tamu.edu}
\,$\bullet$\,
+1\,(469)\,387-3025
\,$\bullet$\,
\href{http://parasol.tamu.edu/~afidel}
{http://parasol.tamu.edu/~afidel}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section{Education}
{Education}

\href{http://www.tamu.edu}
{\textbf{Texas A\&M University}},
College Station, TX, USA

\SmallEntryGap
Doctor of Philosophy (Ph.D.) in
\href{http://cse.tamu.edu}
{Computer Science}
\hfill
\DatestampYMD{2010}{08}{15} --
Present
\begin{detail}
\begin{detail}
Cumulative GPA: 4.0 / 4.0
\end{detail}
Advisors:
Professors Nancy Amato and Lawrence Rauchwerger
\par
Research areas:
High performance computing, parallel algorithms, \par
\hskip 7.3em parallel graph processing.
\par
Dissertation: \emph{Bounded Asynchrony and Nested Parallelism for } \par
\hskip 6.0em \emph{Scalable Graph Processing}
\end{detail}

\EntryGap
\href{http://www.ttu.edu}
{\textbf{Texas Tech University}},
Lubbock, TX, USA
\par
Bachelor of Science (B.S.) in
\href{http://cs.ttu.edu}
{Computer Science}
\hfill
\DatestampYMD{2006}{08}{15} --
\DatestampYMD{2010}{05}{15}
\begin{detail}
Summa Cum Laude
\par
Cumulative GPA: 4.0 / 4.0
\end{detail}


% %%%%%%%%%%%%%%%%%%%%%%%%%
% %% WORK EXPERIENCE %%
% %%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
{Work Experience}

\textbf{Google},
Mountain View, CA, USA
\par
Software Engineer, Ph.D. Intern
\hfill
\DatestampYMD{2015}{09}{28} --
\DatestampYMD{2015}{12}{20}
\begin{detail}
Member of the search infrastructure team.
\par
 Designed and implemented parallel graph mining algorithms for massive scale graphs.
 \par
\end{detail}


% %%%%%%%%%%%%%%%%%%%%%%%%%
% %% RESEARCH EXPERIENCE %%
% %%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research Experience}
{Research Experience}

\textbf{Texas A\&M University - Parasol Lab}, College Station, TX, USA
\par
Research Assistant
\hfill
\DatestampYMD{2010}{05}{15} --
Present
\begin{detail}
\par
\emph{Advisors}: Professors Nancy Amato and Lawrence Rauchwerger
\par
Developer of STAPL, a parallel superset of the C++ Standard Template Library.
\par
Designed, implemented novel graph algorithms and techniques that scale up to 131,072+ cores.
\end{detail}
\EntryGap

\textbf{University of Massachusetts, Amherst}, Amherst, MA, USA
\par
Undergraduate Research Assistant
\hfill
\DatestampYMD{2009}{05}{15} --
\DatestampYMD{2009}{08}{30}
\begin{detail}
\emph{Advisor}: Professor J. Eliot B. Moss
\par
Automatic compiler backend generation targeting JikesRVM.
\par
\end{detail}


% %%%%%%%%%%%%%%%%%%
% %% PUBLICATIONS %%
% %%%%%%%%%%%%%%%%%%

\section{Publications}
{Selected Publications}

\begin{detail}
{{\bf Best Paper Award}. Harshvardhan, \underline{Adam Fidel} Nancy M. Amato, Lawrence Rauchwerger, ``KLA: A New Algorithmic Paradigm for Parallel Graph Computations,'' In Proc. Int. Conf. on Par. Arch. and Comp. Tech. (PACT), Edmonton, Alberta, Canada, Aug 2014.}
\end{detail}

\EntryGap

\begin{detail}
{\underline{Adam Fidel}, Sam Ade Jacobs, Shishir Sharma, Nancy M. Amato, Lawrence Rauchwerger, ``Using Load Balancing to Scalably Parallelize Sampling-Based Motion Planning Algorithms,'' In Proc. Int. Par. and Dist. Proc. Symp. (IPDPS), Phoenix, Arizona, USA, May 2014.}
\end{detail}

\EntryGap

\begin{detail}
{{\bf Best Paper Finalist.} Harshvardhan, \underline{Adam Fidel}, Nancy M. Amato, Lawrence Rauchwerger, ``An Algorithmic Approach to Communication Reduction in Parallel Graph Algorithms,'' In Proc. Int. Conf. on Par. Arch. and Comp. Tech. (PACT), San Francisco, CA, USA, November 2015.}
\end{detail}

\EntryGap

\begin{detail}
{\underline{Adam Fidel}, Francisco Coral Sabido, Colton Riedel, Nancy M. Amato, Lawrence Rauchwerger, ``Fast Approximate Distance Queries in Unweighted Graphs using Bounded Asynchrony,'' In Wkshp. on Lang. and Comp. for Par. Comp. (LCPC), Rochester, NY, USA, September 2016.}
\end{detail}

\section{Skills}
{Skills}

C++ (\emph{Boost, STL}), MPI, OpenMP, Javascript (\emph{Node, React}), Python, Fortran, R
\par
\EntryGap
\href{https://github.com/ledif/}{https://github.com/ledif/}

\end{body}

\end{document}
